---
title: "Interactive Document FISH STYLE Demo:"
runtime: shiny
output: html_document
---

```{r loading stuff, echo=FALSE, message=FALSE, warning=FALSE}
library(shiny)
library(tidyverse)
library(here)
library(leaflet)
library(kableExtra)
library(sf)

```


## Description

Eventually, I hope to build out an app that monitors fish counts for sea run fish in Maine. Below is an extremely rough draft of such an app. 

## This is a markdown document! 

We can do all fun markdown stuff in it like write text, show code chunks, and make html tables:

```{r random content}

2 + 2 


brian.df <- data.frame(
  important.person = "brian"
)

kableExtra::kable(brian.df,
                  col.names = c("People of Import")) %>% 
  kable_styling()


```

## We can also embed shiny apps like the one below

embedding is simple although sometimes of glitchy...the code below works in the context of sourcing multiple apps from different directories. 

```{r shiny app, warning=FALSE, message=FALSE}

shinyAppFile(
  paste0(here(),"/app/app.R"),
  options=list(
    width="100%", height=700
  )
  )


```

